
%======================================================================================================== %


sin(3\pi t) = sin(3\pi (t-2) + 6 \pi )


sin(A + B) = sin (A)Cos(B) + cos(A)Sin(B) 


sin(3\pi (t-2) + 6\pi ) = sin(3\pi (t-2))cos(6\pi ) + cos(3\pi(t-1))sin(6 \pi )


sin(3\pi) = 0              cos(6\pi) = 1


sin(3(t-2) + 6) = sin(3(t-2))


f(t) = sin (3t) +u2(t)sin (3(t-2))


F(s) =(3)2s2+ (3)2-e-2s(3)2s2+ (3)2


F(s) =(1-e-2s)92s2+ 92

 %======================================================================================================== %
 

 

Autumn 0607 Question 1aiii : Periodic function

 

Period of function is 2

 

Base function (b (t))

 

Base function repeated infinitelyf(t) = f(t+p)


Expression can be re-arranged as follows:

 

b(t) =u0(t) +u1(t) -2u2(t) 

 

Laplace transform of base function

 

B(s) =1s+e-ss-2e-2ss 

 

 

Required Laplace transform is derived from base function as follows

 

 

G(s) =11-e-psB(s) 

 

G(s) =11-e-2s1+e-s-2e-2ss 

 

 

 

Let     x =e-s

 

        x2=(e-s)2=e-2s

 

G(s) =11-x21+ x -2x2s

 

G(s) =1x2-12x2-x-1s

 

2x2-x-1 = (2x-1)(x+1)

x2-1 = (x-1)(x+1)

 

 

G(s) =1x-12x-1s 

 

G(s) =2e-s-1s(1-es)
%======================================================================================================== %

Week 8


Inverse Laplace transforms


Q1 - a - i


Q1 - a - ii


Q1 - a - iii


Inverse Laplace transforms


Q1 - b - i


Q1 - b - ii


Q1 - b - iii

Inverse Laplace transforms



Q2 - a

Solving Differential equations using Laplace transforms


Q2 - b 

Solving Integral equations using Laplace transforms



base function B(s)


Base function repeated infinitelyf(t) = f(t+p)


11-e-ps


G(s)  = \frac{B(s)}{}


 

Part 4 Solving ODEs using Laplace Transforms 

 

d2ydt2+dydt+ y = 1 + t 

 

Alternative notation

 

d2ydt2y(t)                dydty(t)


Initial Conditions are often (but not always) zero    y(0) = 0y(0) = 0

 

 

y+y+ y = 1 + t

 

L[y] =s2Y(s) - sy(0)-y(0)            note the initial conditions. L[y] =s2Y(s)

 

L[y] = sY(s) - y(0)                           note the initial conditions. L[y] = sY(s) 

 

L[ y] = Y(s)

 

Ld2ydt2+dydt+ y=(s2+s+1)Y(s)    Quadratic Term multiplied by Y(s)


 

 



f(t) =u0(t) -u1(t)[sin (3t)] = sin (3t) -u1(t)sin (3t)


sin(3t) = sin(3(t-1) + 3)


sin(A + B) = sin (A)Cos(B) + cos(A)Sin(B) 


sin(3(t-1) + 3) = sin(3(t-1))cos(3) + cos(3(t-1))sin(3)


sin(3) = 0              cos(3) = -1


sin(3(t-1) + 3) = -sin(3(t-1))


f(t) = sin (3t) +u1(t)sin (3(t-1))


F(s) =(3)2s2+ (3)2+e-s(3)2s2+ (3)2


F(s) =(1+e-s)92s2+ 92


 

End of Year Exam  2009 Question 1bi


Find the inverse laplace transform of G(s)


G(s) =2s-4s2- s - 6


s2- s - 6 = (s-3)(s+2)


G(s) =2s(s-2)(s+3)-4(s-2)(s+3)


entry no 12 and 13 with a =3 and b =  -2



End of Year Exam  2009 Question 1b(ii)

Find the inverse laplace transform of G(s)


G(s) =e-4ss2- 3s



G(s)in forme-asF(s)witha = 4.



F(s) =1(s)(s-3)



f(t) =13[e3t- 1 ]


End of Year Exam  2008 Question 1b(iii)


Find the inverse laplace transform of G(s)


G(s) =tan-1(s)


tan-1(s) ds


%======================================================================================================== %

\newpage 
Example 1

Find g(t), the inverse Laplace transform of G(s) =2s3

Consider this in form G(s) = -F(s)

Necessarily 

 

Finding the inverse Laplace transform of F(s)

 

f(t) = t

 


g(t) = tf(t) =t2

 

Summary:

∙       Given G(s), we consider it in form G(s) =-F(s)

∙       We negate G(s) and integrate it to find F(s).

∙       We get the inverse laplace transform of F(s) to find f(t).

∙       We multiply f(t) by ‘t’ to find g(t)

 
%======================================================================================================== %

Example 2

Find the inverse Laplace transform of lnss-1

 

To solve this we use a same approach to the one in the previous example, but in reverse.

 

∙       We consider the given equation in form F(s).

∙       We negate F(s) and differentiate it to find G(s).

∙       We get the inverse Laplace transform of G(s) , yielding g(t).

∙       We divide g(t) by ‘t’ to find f(t)

 

 F(s) = lnss-1= ln(s) - ln(s-1)           

G(s) =-F(s) = -dds( ln(s)) +dds(ln(s-1))


G(s) =dds( ln(s-1)) -dds(ln(s))


G(s) =1s-1-1s


g(t) =et- 1


f(t) =g(t)t=et- 1t



 

G(s) = lns2s2-1


 lns2s2-1=ln(s2) -ln(s2-1)


ln(s2) = 2ln(s)



dds2ln(s) =2s



To compute  ddsln(s2- 1), apply the chain rule.



ddsln(s2- 1) = 2s1s2-1 


 F(s) =2ss2-1-2s



 g(t) = 2 cos(t) -2


f(t) =g(t)t=2 cos(t) -2t
%======================================================================================================== %


Laplace Question 1bii

 

 

k(s-a)(s-b)=ka-bs-a+-ka-bs-b

 

 

s(s-a)(s-b)=a+ka-bs-a+-b-ka-bs-b

%======================================================================================================== %
\subsection*{Example 4}
Find the inverse Laplace transform of  F(s)


\[ F(s) =tan-1(s)\]


G(s) =-F(s) = -ddstan-1(s)


G(s) =-1s2-1


g(t) = -sin(t)


f(t) =g(t)t=-sin(t)t

 

\newpage 

Using Laplace transforms to solve integral equations#

 

 y(t) = 1+t+0tcos(t-u).y(u)du

 

L[y(t)] = Y(s)

 

L[1+t] =1s+1s2=s+1s2

 

L[0tcos(t-u).y(u)du] =L[cos(t)]L[y(t)] =s Y(s)s2+1

 

Y(s) =s+1s2+s Y(s)s2+1

 

(s2+1) Y(s)s2+1-s Y(s)s2+1=s+1s2

 

(s^2-s +1) Y(s)s2+1=s+1s2

 

 


 \[ y(t) = cos(t)+ 20tsin(t-u).y(u)du\]


 

 

L[y(t)] = Y(s)

 

L[cos(t)] =ss2-1

 

L[0tcos(t-u).y(u)du] =L[cos(t)]L[y(t)] =s Y(s)s2+1


\end{document}